Digital History in Finland, 1488-1828

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

@@

# Selected time spam
df0 = bind_rows(fen, kun)
df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
```

@@

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10, out.width="430px"}
df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
p <- ggplot(df2, aes(x = publication_decade, y = n)) +
     #geom_bar(stat = "identity") + #scale_y_log10() +
     geom_line(aes(linetype = catalog)) +
     geom_point(aes(shape = catalog), size = 3) +     
     #ylab("Paper consumption (km2)")
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle("Overall publishing activity")
print(p)
```

@@

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=8, fig.height=6, fig.show="hold", out.width="430px"}
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
               #summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%	       
	       filter(publication_place %in% selected.places) # %>%
	       #filter(publication_decade >= 1600)
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = spread(df2, publication_decade, n, fill = 0)
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {

  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     #scale_y_log10() +
     #facet_wrap(catalog ~ .) + 
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal)
  print(p)

@@

  # Use timeinterval year intervals
  dfsel = subset(df0, catalog == catal)
  #dfsel = subset(df0, publication_place == "Stockholm")
  #dfsel = subset(df0, publication_place == "Norrköping")
  #dfsel = subset(df0, publication_place == "Gävle")

@@

langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0

@@

theme_set(theme_bw(20))
p <- ggplot(dfs, aes(x = publication_year, y = n)) +
       geom_point(size = 2) +
       #geom_line() +
       geom_smooth(col = "black") +              
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))       
print(p)

@@

theme_set(theme_bw(20))
p <- ggplot(dfs, aes(x = publication_year, y = paper)) +
       geom_point(size = 2) +
       #geom_line() +
       geom_smooth(col = "black") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))
print(p)

@@

  # Selected catalogue with selected topics
  df <- df %>% filter(catalog == catalogue & hit)
  lang <- paste("language.", langs, sep = "")
  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
  dfl <- NULL
  for (lan in lang) {
    # Classify a document to the specifed language
    # If document is assigned with languages, each case is considered
    # so one doc may have multiple entries corresponding to different languages
    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
    # Combine data frames for specified languages
    dflsub <- filter(df, df[[lan]])
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
  dfl$language <- factor(dfl$language, levels = langs)

@@

  # TITLE COUNT
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       # geom_smooth(aes(col = language)) + 
       xlab("Publication year") +
       ylab("Title count (n)") +
       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
  print(p)

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       # geom_smooth(aes(col = language)) + 
       xlab("Publication year") +
       ylab("Paper consumption") +
       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
       ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
  print(p)
```

@@

  # TITLE COUNT
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
  print(p)

@@

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
sel <- c("hautajaiset", "häät", "juhlamenot")

catalogue <- "Fennica"
  if (catalogue == "Fennica") {
    df <- df.full # full time span
  } else if (catalogue == "Kungliga") {
    df <- df0 # selected time span
  }
  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)

@@

langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  dflsub$language <- gsub("language.", "", lan)
  dfl <- bind_rows(dfl, dflsub)
}
dfl$language <- factor(dfl$language, levels = langs)

@@

langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
df$language[!df$language %in% langs] <- "Other"
df$language <- factor(df$language, levels = langs)

>>>>

```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

@@

# Selected time spam
df0 = bind_rows(fen, kun)
df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))

langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
```

@@

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10, out.width="430px"}
df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
p <- ggplot(df2, aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = catalog)) +
     geom_point(aes(shape = catalog), size = 3) +     
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle("Overall publishing activity")
print(p)
```

@@

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=8, fig.height=6, fig.show="hold", out.width="430px"}
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) # %>%
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = spread(df2, publication_decade, n, fill = 0)
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {

  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
     geom_line(aes(linetype = publication_place)) +
     geom_point(aes(shape = publication_place), size = 3) +
     ylab("Title count (n)") + xlab("Publication year") +  
     ggtitle(catal)
  print(p)

@@

  # Use timeinterval year intervals
  dfsel = subset(df0, catalog == catal)

@@

@@

theme_set(theme_bw(20))
p <- ggplot(dfs, aes(x = publication_year, y = n)) +
       geom_point(size = 2) +
       geom_smooth(col = "black") +              
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))       
print(p)

@@

theme_set(theme_bw(20))
p <- ggplot(dfs, aes(x = publication_year, y = paper)) +
       geom_point(size = 2) +
       geom_smooth(col = "black") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))
print(p)

@@

  # Selected catalogue with selected topics
  df <- df %>% filter(catalog == catalogue & hit)
  lang <- paste("language.", langs, sep = "")
  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
  dfl <- NULL
  for (lan in lang) {
    # Classify a document to the specifed language
    # If document is assigned with languages, each case is considered
    # so one doc may have multiple entries corresponding to different languages
    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
    # Combine data frames for specified languages
    dflsub <- filter(df, df[[lan]])
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
  print(p)
```

@@

@@

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
sel <- c("hautajaiset", "häät", "juhlamenot")
catalogue <- "Fennica"
df <- df.full # full time span
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
# Selected catalogue with selected topics
df <- df %>% filter(catalog == catalogue & hit)
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  dflsub$language <- gsub("language.", "", lan)
  dfl <- bind_rows(dfl, dflsub)
}
df <- dfl %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

@@

df$language[!df$language %in% langs] <- "Other"
df$language <- factor(df$language, levels = langs)
